Building Markov State Model for a Periodically Driven Non-Equilibrium System

### 2014-08-15 writedown/period.noneq.msm/main.tex
backup

\documentclass[preprint,unsortedaddress,a4paper,onecolumn]{revtex4-1}
% \documentclass[acs, jctcce, a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
% \documentclass[aps,pre,twocolumn,unsortedaddress]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

@@

@@

\begin{table}
  \centering
  \caption{The first non-trivial timescales calculated from $e^{T\vect B}$.
  }
  \begin{tabular*}{0.3\textwidth}{@{\extracolsep{\fill}}c   c}\hline\hline
    Method      &        $t_2$ [ps]  \\\hline
    5 sets      & 72.4     \\
    Uni. $M=05$ & 53.6     \\
    Uni. $M=10$ &107.2     \\
    Uni. $M=20$ &113.8     \\
    Uni. $M=30$ &120.6     \\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp1}
\end{table}

@@

@@

where $V$ is the time-dependent and $t$-periodic potential. For simplicity we denote the force by $F(x_t,t) = -\nabla_x V(x_t, t)$. $dw_t$ is
the standard Wiener process.  Assuming a discretization of the

@@

$t_i = iT / N$. We denote $x_i = x_{t_i}$, and $w_i = w_{t_i}$, then we have the
conditional probability:
  p(x_T,T\vert x_0,0) =\lim_{N\rightarrow\infty} &\,
  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_1\cdots\int dx_{N-1}\\\nonumber
  \exp\bigg\{\frac1\sigma\sum_{i=0}^{N-1} F(x_i,t_i)(w_{i+1} - w_{i}) - \frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_i,t_i)\dt\bigg\} \times\\\label{eqn:tmp8}
  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=0}^{N-1} \frac{(x_{i+1} - x_i)^2}{\dt}\bigg\}.
Notice that
\begin{align}\label{eqn:tmp10}
  \sigma(w_{i+1} - w_{i}) =
  x_{i+1} - x_i 
we have
% so with the formal identity $(dw_t)^2 = dt$,  we have
  p(x_T,T\vert x_0,0)
  =\lim_{N\rightarrow\infty} &\,
  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_1\cdots\int dx_{N-1}\\\nonumber
  \exp\bigg\{\frac1{\sigma^2}\sum_{i=0}^{N-1} F(x_{i},t_{i})(x_{i+1} - x_i) -\frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_i,t_i)\dt\bigg\} \times\\\label{eqn:tmp10}
  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=0}^{N-1} \frac{(x_{i+1} - x_i)^2}{\dt}\bigg\}.

@@

Since we have the symmetry $F(x_t, -t) = -F(x_t, t)$, the conjugate dynamics also satisfies Eq.~\eqref{eqn:tmp7}.
Therefore, we have the probability:
  p(x_0,T\vert x_T,0) = &\,
  p^\dagger(x^\dagger_T,T\vert x^\dagger_0,0)  \\\nonumber
  = &\,
  \lim_{N\rightarrow\infty}
  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx^\dagger_1\cdots\int dx^\dagger_{N-1}\\\nonumber
  \exp\bigg\{\frac1{\sigma^2}\sum_{i=0}^{N-1} F^\dagger(x^\dagger_{i},t_{i})(x^\dagger_{i+1} - x^\dagger_i) -\frac1{2\sigma^2}\sum_{i=0}^{N-1}[F^\dagger(x^\dagger_i,t_i)]^2\dt\bigg\} \times\\\nonumber
  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=0}^{N-1} \frac{(x^\dagger_{i+1} - x^\dagger_i)^2}{\dt}\bigg\} \\\nonumber
  \lim_{N\rightarrow\infty} 
  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_1\cdots\int dx_{N-1}\\\nonumber
  \exp\bigg\{\frac1{\sigma^2}\sum_{i=N}^{1} F(x_{i},t_{i})(x_{i-1} - x_i) -\frac1{2\sigma^2}\sum_{i=N}^{1}F^2(x_i,t_i)\dt\bigg\} \times\\\label{eqn:tmp11}
  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=N}^{1} \frac{(x_{i-1} - x_i)^2}{\dt}\bigg\}.

@@

  \log\bigg\{\frac{  p[x_t] }{ p[x^\dagger_t]} \bigg\}
  \frac1{\sigma^2}\sum_{i=1}^{N-1} F(x_i,t_i)(x_{i+1} - x_{i}) + F(x_i,t_i)(x_{i} - x_{i-1}) 

@@

Now consider the differentiation:

@@

@@

  \log\bigg\{\frac{  p[x_t] }{ p[x^\dagger_t]} \bigg\}
  \frac2{\sigma^2}\sum_{i=0}^{N-1} F(x_i,t_i)(x_{i+1} - x_{i}) +
  \frac1{\sigma^2}\sum_{i=0}^{N-1}\nabla_xF(x_i,t_i)(x_{i+1} - x_{i})^2

@@

We notice that
  dV(x, t) = &\, \frac{\partial V}{\partial x} dx + \frac{\partial V}{\partial t} dt\\\nonumber
  \frac12 \sigma^2 \nabla^2_x V dt +  \nabla V dx_t + \frac{\partial V}{\partial t} dt \\
  -\frac12 \sigma^2 \nabla_x F dt -  F dx_t + \frac{\partial V}{\partial t} dt

@@

and the identity
  dt = (dw_t)^2 = \frac1{\sigma^2} dx_t^2
Eq.~\eqref{eqn:tmp14} becomes
  \log\bigg\{\frac{  p[x_t] }{ p[x^\dagger_t]} \bigg\}
  -\frac2{\sigma^2}\bigg[
  V(x_N,t_N) - V(x_0,t_0) + \sum_{i=0}^{N-1}\partial_tV(x_i,t_i)\dt
According to the  Einstein relation $T = \sigma^2/2$, by denoting $\beta = 1/T$
  \log\bigg\{\frac{  p[x_t] }{ p[x^\dagger_t]} \bigg\}
  -\beta\bigg[
  V(x_N,t_N) - V(x_0,t_0) + \sum_{i=0}^{N-1}\partial_tV(x_i,t_i)\dt
Therefore
  p(x_0,T\vert x_T,0)
  % \lim_{N\rightarrow\infty} 
  % \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_{N-1}\cdots\int dx_{1}
  \int_{\mc\{x_0,0;x_T,T\}}
  \frac{  p[x^\dagger_t] }{ p[x_t]} \cdot p[x_t] \\\label{eqn:tmp19}
  = &\,
  \frac{e^{-\beta V(x_0,t_0)}}{e^{-\beta V(x_N,t_N)}}
  \int_{\mc\{x_0,0;x_T,T\}}
  \beta\int_0^T \partial_t V(x_t,t)dt 
  \bigg\} \cdot p[x_t]
where $\mc\{x_0,0;x_T,T\}$ denotes all continuous trajectories starting at $x_0$ and ending at $x_T$.
If $\partial_t V = 0$, i.e.~equilibrium, we have
  p(x_0,T\vert x_T,0)e^{-\beta V(x_T,T)} =  p(x_T,T\vert x_0,0) e^{-\beta V(x_0,0)},
which proves the reversibility of the equilibrium dynamics.
The term
  W[x_t] = - \int_0^T \partial_t V(x_t,t)dt
is the non-equilibrium work associated to all possible
the dynamics $x_t$ starting at $x_0$ and ending at $x_T$ (see e.g.~Ref.~\cite{seifert2012stochastic}).
Therefore Eq.~\eqref{eqn:tmp19} is the detailed Jarzynski relation.
Now the problem becomes if we can write a nice form (e.g.~the difference of a state function measured at $x_T$ and $x_0$) for the non-equilibrium work.

>>>>

\documentclass[aps, pre, preprint,unsortedaddress,a4paper,onecolumn]{revtex4-1}
% \documentclass[acs, jctcce, a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
% \documentclass[aps,pre,twocolumn,unsortedaddress]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

@@

\section{Introduction}
Non-equilibrium, especically periodically driven system. Interesting.

MSM tools for analyzing, provide profund understanding.

Current achievement of MSM in equilibrium cases.

Importance: first application of MSM in a non-equilibrium system.

@@

\begin{table}
  \centering
  \caption{The first four non-trivial timescales calculated from $e^{T\vect B}$. The unit of time in the table is ps.
    $\tau$ is the lag time used to calculate the generator~\eqref{eqn:tmp4}. $[T_0,T_1]$ is the time interval,
    in which the generator is estimated from the MD trajectories. The 5th eigenvalue of uniform decomposition with $\tau=8.0$~ps is not real, so
    the corresponding timescale is not calculated.
  }
  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}c ccc rrrr}\hline\hline
    Method  &  $M$ & $\tau$ & $[T_0,T_1]$ &   $t_2$ &   $t_3$ &   $t_4$ &   $t_5$  \\\hline
    5 sets  & --   & 0.5    & $[300,1000]$    &  72.4 & 17.8 &  2.1 & 2.8    \\
    Uniform & $05$ & 0.5    & $[300,1000]$    &  53.6 & 17.4 &  9.4 & 2.8    \\
    Uniform & $10$ & 0.5    & $[300,1000]$    & 107.2 & 27.0 & 16.4 & 3.6    \\
    Uniform & $20$ & 0.5    & $[300,1000]$    & 118.6 & 30.4 & 20.3 & 4.3    \\
    Uniform & $30$ & 0.5    & $[300,1000]$    & 120.6 & 31.1 & 20.9 & 4.4    \\\hline
    Uniform & $20$ & 0.5    & $[0,40]$    & 156.5 & 34.4 & 20.7 & 4.4    \\
    Uniform & $20$ & 0.5    & $[0,80]$    & 133.8 & 32.8 & 20.4 & 4.4    \\
    Uniform & $20$ & 0.5    & $[0,120]$   & 127.5 & 32.0 & 20.3 & 4.3    \\
    Uniform & $20$ & 0.5    & $[0,200]$   & 122.0 & 31.3 & 20.3 & 4.3    \\
    Uniform & $20$ & 0.5    & $[0,320]$   & 120.4 & 31.0 & 20.3 & 4.3    \\\hline
    Uniform & $20$ & 1.0    & $[300,1000]$    & 119.8 & 30.5 & 21.7 & 4.9   \\
    Uniform & $20$ & 2.0    & $[300,1000]$    & 117.8 & 29.2 & 21.5 & 5.3   \\
    Uniform & $20$ & 4.0    & $[300,1000]$    & 114.2 & 27.0 & 20.2 & 4.8   \\
    Uniform & $20$ & 8.0    & $[300,1000]$    & 110.6 & 25.0 & 18.1 & --   \\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp1}
\end{table}

\section{Discussions}
\subsection{The periodicity of the reduced dynamics}

As discussed before, if the reduced dynamics captures the slow
dynamics of interest, then the reduced dynamics is also periodic,
which implies that the generator $M(t)$ can be estimated from any time
interval by Eq.~\eqref{eqn:tmp4}. In practice, the reduced dynamics
may not be perfectly periodic. The generator calculated from
different time intervals can be used to test the periodicity of the
reduced dynamics. The results are shown in Tab.~\ref{tab:tmp1} and
Fig.~\ref{fig:tmp2}.  The dependency with respect to the time
interval, in which the generator is calculated, indicates the reduced
dynamics is not perfectly periodic. The reduced dynamics from $[0,40]$
reproduces the best probability in interval $[0,40]$, and worst in the
steady state. Moreover, the leading non-trivial timescale is also off
(see Tab.~\ref{tab:tmp1}), while the accuracy of the second and third
non-trivial timescales are better, because they are comparable to the
period, 40~ps, in which the dynamics is relaxed. The reduced dynamics
from $[300,1000]$ reproduces the best steady state probability, while
worst in reproducing the initial relaxation process. The reduced
dynamics from $[0,320]$ is indistinguishable from the one from
$[300,1000]$, which implies that in practice, one only have to
simulation relatively short non-equilibrium trajectories (that are
almost relaxed), and compute the generator from it to build the reduced dynamics. \redc{This saves a great
amount of computational resources comparing with calculating the
reduced dynamics only from steady state trajectories.}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{fig/t040/fig-cg-prob-range.eps}  
  \caption{The time-dependent probability of conformation
    $\confc$. The brute force MD simulation is compared with reduced
    dynamics, the transition matrix of which are calculated from
    different ranges. The red shadow region is the statistical uncertainty of the brute force MD simulation.
    The inserts show the zoom-ined probability at the relaxation stage $[0,120 ]~\textrm{ps}$ and at the steady state $[800,880 ]~\textrm{ps}$.}
  \label{fig:tmp2}
\end{figure}

\subsection{The choice of lag time $\tau$}
Table~\ref{tab:tmp1} shows a clear trend of worse accuracy with
increased $\tau$, however, the timescales are not very sensitive to
the choice of lag time $\tau$.

@@

\section{Numerical results}
\subsection{Steady state distribution}
\begin{figure}
  \centering  
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist-msm.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-1.eps}
  \caption{The steady state distribution calculated by brute force non-equilibrium comparing with MSM.}
  \label{fig:num-1}
\end{figure}
\begin{figure}
  \centering  
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-2-simple.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-3-simple.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-4-simple.eps}
  \caption{The steady state distribution calculated by brute force non-equilibrium comparing with MSM.}
  \label{fig:num-2}
\end{figure}

\subsection{Committors}
\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-1.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-1.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-1.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-1.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-1.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-1.eps}
  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-2.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-2.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-2.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-2.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-2.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-2.eps}
  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-3.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-3.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-3.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-3.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-3.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-3.eps}
  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
  \label{fig:num-2}
\end{figure}

@@

where $V$ is the time-dependent and $T$-periodic potential. For simplicity we denote the force by $F(x_t,t) = -\nabla_x V(x_t, t)$. $dw_t$ is
the standard Wiener process.
According to Girsanov, we have
  \label{eq:tmp8}
  \frac{dp[x_t]}{dw[x_t]}  =
  \exp \bigg\{
  \frac 1{\sigma^2}\int_0^T F(x_t,t) dx_t -
  \frac1{2\sigma^2}\int_0^T F^2(x_t,t) dt
  \bigg\}
where $dp$ is the probability measure of trajectory $x_t$, while $dw$ is the
probability measure of the standard Wiener process $dx_t = \sigma dw_t$.
Assuming a discretization of the

@@

$t_i = iT / N$. We denote $x_i = x_{t_i}$, and $w_i = w_{t_i}$, then we have,
in the sense of Ito,
\begin{align}\label{eq:tmp9}
  \frac{dp[x_t]}{dw[x_t]}  \approx
  \exp\bigg\{\frac1{\sigma^2}\sum_{i=0}^{N-1} F(x_{i},t_{i})(x_{i+1} - x_i) -\frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_i,t_i)\dt\bigg\} 

@@

Writting the Girsanov for the conjugate dynamics
\begin{align}\label{eq:dagger-0}
  \frac{dp^\dagger[x^\dagger_t]}{dw[x^\dagger_t]}  
  \approx\,&
  \frac1{\sigma^2}\sum_{i=0}^{N-1} F^\dagger(x^\dagger_{i},t_{i})(x^\dagger_{i+1} - x^\dagger_i) -
  \frac1{2\sigma^2}\sum_{i=0}^{N-1}[F^\dagger(x^\dagger_i,t_i)]^2\dt\bigg\} \\ \nonumber
  =\,&
  \frac1{\sigma^2}\sum_{i=0}^{N-1} F(x^\dagger_{i},T - t_{i})(x^\dagger_{i+1} - x^\dagger_i) -
  \frac1{2\sigma^2}\sum_{i=0}^{N-1}[F(x^\dagger_i, T-t_i)]^2\dt\bigg\} \\\nonumber
  =\,&
  \frac1{\sigma^2}\sum_{i=0}^{N-1} F(x_{N-i},t_{N-i})(x_{N-i-1} - x_{N-i}) -
  \frac1{2\sigma^2}\sum_{i=0}^{N-1}[F(x_{N-i},t_{N-i})]^2\dt\bigg\} \\
  = \,&
  \frac1{\sigma^2}\sum_{i=N}^{1} F(x_{i},t_{i})(x_{i-1} - x_i) -
  \frac1{2\sigma^2}\sum_{i=N}^{1}F^2(x_i,t_i)\dt\bigg\}
% Therefore,
% \begin{align}\nonumber
%   \frac{dp[x^\dagger_t]}{dw[x^\dagger_t]}  =
%   \,&
%   \frac{dp^\dagger[x^\dagger_t]}{dw[x^\dagger_t]} \\\nonumber
%   \approx\,&
%   \exp\bigg\{
%   \frac1{\sigma^2}\sum_{i=0}^{N-1} F^\dagger(x^\dagger_{i},t_{i})(x^\dagger_{i+1} - x^\dagger_i) -
%   \frac1{2\sigma^2}\sum_{i=0}^{N-1}[F^\dagger(x^\dagger_i,t_i)]^2\dt\bigg\} \\\nonumber
% \end{align}
Since it is obvious that $dw[x^\dagger_t] / dw[x_t] = 1$,
  \label{eq:tmp10}
  \frac{dp^\dagger[x^\dagger_t]}{dw[x_t]}
  \approx \,&
  \frac1{\sigma^2}\sum_{i=1}^{N} F(x_{i},t_{i})(x_{i-1} - x_i) -
  \frac1{2\sigma^2}\sum_{i=1}^{N}F^2(x_i,t_i)\dt\bigg\}

@@

  \frac{  dp^\dagger[x^\dagger_t] }{ dp[x_t]}
  \approx&\,
  -\frac1{\sigma^2}\sum_{i=1}^{N-1}
  \bigg[
  F(x_i,t_i)(x_{i+1} - x_{i}) + F(x_i,t_i)(x_{i} - x_{i-1})
  \bigg\}

@@

Assuming the smoothness of the external perturbation, consider the differentiation:

@@

The second order expansion w.r.t.~$x_i - x_{i-1}$ is of order $\dt$, so it is absorbed into $ \mo(\dt)$.

@@

  \frac{  dp^\dagger[x^\dagger_t] }{ dp[x_t]}
  \approx&\,
 -\frac2{\sigma^2}\sum_{i=0}^{N-1} F(x_i,t_i)(x_{i+1} - x_{i}) 
 -\frac1{\sigma^2}\sum_{i=0}^{N-1}\nabla_xF(x_i,t_i)(x_{i+1} - x_{i})^2
 \bigg\}

@@

Using the identity
$  dt = (dw_t)^2 = {\sigma^{-2}} dx_t^2$,
Eq.~\eqref{eqn:tmp14} is written in the integral form
\begin{align}\label{eqn:tmp14-0}
  \frac{  dp^\dagger[x^\dagger_t] }{ dp[x_t]}
  \approx&\,
 -\frac2{\sigma^2}\int_0^T F(x_t,t) dx_t
 -\int_0^T\nabla_xF(x_t,t)dt
 \bigg\}  

@@

One would not have the second integral on the exponent if the first integral of the exponent were defined in the sense of Stratonovich.

We notice that
\begin{align}\nonumber
  dV(x, t) = &\, \frac{\partial V}{\partial x} dx + \frac{\partial V}{\partial t} dt\\\nonumber
  =&\,
  \frac12 \sigma^2 \nabla^2_x V dt +  \nabla V dx_t + \frac{\partial V}{\partial t} dt \\
  =&\,
  -\frac12 \sigma^2 \nabla_x F dt -  F dx_t + \frac{\partial V}{\partial t} dt
\end{align}
Eq.~\eqref{eqn:tmp14-0} becomes
\begin{align}
  \frac{  dp^\dagger[x^\dagger_t] }{ dp[x_t]}
  =&\,
  \exp\bigg\{
  \frac2{\sigma^2}\bigg[
  V(x_T,T) - V(x_0,t_0) - \int_0^T\partial_tV(x_t,t)dt
  \bigg]
  \bigg\}
\end{align}
According to the  Einstein relation, the temperature $\mathcal T = \sigma^2/2$, we denote $\beta = 1/{\mathcal T} = 2/\sigma^2$.
Take the limit of infinite small time interval, and notice the equilibrium
invariant probability density with respect to potential $V(x,0)$ satisfies $\mu(x) \propto e^{-\beta V(x,0)}$,
\begin{align}
  \frac{  dp^\dagger[x^\dagger_t] }{ dp[x_t]}
  =&\,
  \frac{\mu(x_0)}{\mu(x_T)}\times
  \exp\bigg\{
  - \beta\int_0^T\partial_tV(x_t,t)dt
  \bigg\}
\end{align}

In Eq.~\eqref{eq:dagger-0}, we assume the periodicity of the perturbation $F(x,t) = F(x,t+T)$, and the symmetry of the external perturbation, i.e.~$F(x, -t) = F(x, t)$, we have
\begin{align}
  \frac{dp^\dagger[x^\dagger_t]}{dw[x^\dagger_t]}  
  \approx\,&
  \exp\bigg\{
  \frac1{\sigma^2}\sum_{i=0}^{N-1} F(x^\dagger_{i},t_{i})(x^\dagger_{i+1} - x^\dagger_i) -
  \frac1{2\sigma^2}\sum_{i=0}^{N-1}[F(x^\dagger_i, t_i)]^2\dt\bigg\}  
\end{align}
By changing notation $x^\dagger$ back to $x$, and comparing with~\eqref{eq:tmp9}, the reversed dynamics is subject to the Eq.~\eqref{eqn:tmp7},
i.e.~$dp^\dagger = dp$.
Therefore
\begin{align}\nonumber
  p(x_0,T\vert x_T,0)
  =&\,\int_{\mc\{x_T,0;x_0,T\}}
  dp[x^\dagger_t] \\\nonumber  
  =&\,
  \int_{\mc\{x_0,0;x_T,T\}}
  \frac{  dp[x^\dagger_t] }{ dp[x_t]} \cdot dp[x_t] \\\nonumber
  =&\,
  % \lim_{N\rightarrow\infty} 
  % \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_{N-1}\cdots\int dx_{1}
  \int_{\mc\{x_0,0;x_T,T\}}
  \frac{  dp^\dagger[x^\dagger_t] }{ dp[x_t]} \cdot dp[x_t] \\\label{eqn:tmp18}
  = &\,
  \frac{\mu(x_0)}{\mu(x_T)}
  \int_{\mc\{x_0,0;x_T,T\}}
  \exp\bigg\{
  -\beta\int_0^T \partial_t V(x_t,t)dt 
  \bigg\} \cdot dp[x_t]
\end{align}
where $\mc\{x_0,0;x_T,T\}$ denotes all continuous trajectories starting at $x_0$ and ending at $x_T$.
If $\partial_t V = 0$, i.e.~equilibrium, we have
\begin{align}
  p(x_0,T\vert x_T,0)e^{-\beta V(x_T,T)} =  p(x_T,T\vert x_0,0) e^{-\beta V(x_0,0)},
\end{align}
which proves the reversibility of the equilibrium dynamics.
The term
\begin{align}
  W[x_t] = \int_0^T \partial_t V(x_t,t)dt
\end{align}
is the non-equilibrium work associated to all possible
the dynamics $x_t$ starting at $x_0$ and ending at $x_T$ (see e.g.~Ref.~\cite{seifert2012stochastic}).
Therefore Eq.~\eqref{eqn:tmp18} is the detailed Jarzynski relation.
% Now the problem becomes if we can write a nice form (e.g.~the difference of a state function measured at $x_T$ and $x_0$) for the non-equilibrium work.
Noticing that
\begin{align}
  \label{eq:tmp21}
  p(x_T,T\vert x_0,0) = \int_{\mc\{x_0,0;x_T,T\}}dp[x_t],
\end{align}
From Eq.~\eqref{eqn:tmp18} we have
\begin{align}
  \label{eq:tmp22}
  \frac{p(x_0,T\vert x_T,0)}{  p(x_T,T\vert x_0,0)  }
  =
  \frac{\mu(x_0)}{\mu(x_T)}
  \mathbb E_{x_0\rightarrow x_T} [e^{-\beta W}]
\end{align}
% Maybe we want a more symmetric form.
% The expectation value of the reversed dynamics reads,
% \begin{align}\nonumber
%   \mathbb E_{x^\dagger_0\rightarrow x^\dagger_T} [e^{-\beta W^\dagger}]
%   =\,&
%   \int_{\mc\{x^\dagger_0,0;x^\dagger_T,T\}}
%   \exp\bigg\{
%   -\beta\int_0^T \partial_t V(x^\dagger_t,t)dt 
%   \bigg\} \cdot dp[x^\dagger_t]   \\\nonumber
%   =\,&
%   \int_{\mc\{x_0,0;x_T,T\}}
%   \exp\bigg\{
%   -\beta\int_0^T \partial_t V(x_{T-t},t)dt 
%   -\beta\int_0^T \partial_t V(x_{t},t)dt 
%   \bigg\}
%   \cdot dp[x_t]   \\  \nonumber
%   =\,&
%   \int_{\mc\{x_T,0;x_0,T\}}
%   \exp\bigg\{
%   \beta\int_0^T \partial_t V(x_t,t)dt 
%   \bigg\} \cdot dp[x_t]   \\
%   \label{eq:tmp23}
%   = \,&
%   \mathbb E_{x_0\rightarrow x_T} [e^{- 2\beta W}]  
% \end{align}
% Noticing that \eqref{eq:tmp22}  is true for the reversed dynamics, we have
% \begin{align}
%   \label{eq:24}
%   \frac{p(x_T,T\vert x_0,0)}{  p(x_0,T\vert x_T,0)  }
%   =
%   \frac{\mu(x_T)}{\mu(x_0)}
%   \mathbb E_{x_T\rightarrow x_0} [e^{\beta W}]  
% \end{align}
